Verifying Cache Coherence Protocols for an Infinite Family of Cache Hierarchies

### 2014-02-06 paper/Intuition.tex
stuff

Invariants~\fullref{conservative} and \fullref{localCompatibility1} defines a
$\ge$ relation between the states of a parent and its child for any address.
Since the ancestor relation is the reflexive-transitive closure of the parent
relation, the $\ge$ relation is preserved between the states of two caches $p$
and $c$ where $p$ is the ancestor of $c$.

@@

We prove Invariant~\fullref{latestValue} by strong induction on time. Consider
two cases: (a) cache $c$ is already \clean{} for an address $a$ at time $t$ or
(b) the contrary.  If \clean{}, then it has the latest value at time $t$. Since
none of its children's directory entries can be in \Mo{}, all its descendants
should be no greater than \Sh{} for that address (because of Invariant~\fullref{conservative} and the fact that the $\ge$ relation is preserved for the
state of a cache and that of its ancestor). Any non-ancestor of $c$ and
non-descendant of $c$ must be compatible (as discussed in the previous
paragraph).  Since $c$ is \clean, it is at least in the \Sh{} state, so
compatibility means that non-descendants cannot be in \Mo{} state. All of
$c$'s ancestors are non-leaves, so they cannot process any store requests.
Therefore, no cache save $c$ may have processed a store request, which means that
$c$ contains the latest value for address $a$ at time $t+1$ if it was \clean{}
at time $t$.

If $c$ was not clean at time $t$, it must have received data from either its
parent or its child, and the sender is \clean{} by Invariant~\ref{noTransitWrite}. By the induction hypothesis, it means that the sender has
the latest value for the address. Again, because of
Invariant~\ref{noTransitWrite}, no store request can be processed when the data
is in transit, which means $c$ will have the latest value for address $a$ at
time $t+1$, establishing Invariant~\fullref{latestValue}.

>>>>

Invariants~\fullref{conservative} and \fullref{localCompatibility1} define a
$\ge$ relation between the states of a parent and its child for any address.
Since the ancestor relation is the reflexive-transitive closure of the parent
relation, the $\ge$ relation is preserved between the states of two caches $p$
and $c$ where $p$ is the ancestor of $c$.

@@

Using the properties discussed in the last two paragraphs, it is easy to prove
Invariant~\ref{latestValue}. The proof is by induction on time $t$. We consider
the cases when a node is either \clean{} in the previous state or not. One can
easily prove that if it was \clean{} in the previous state, then no cache, save
itself, can process a store request, proving the invariant.  If the cache was
not \clean{} in the previous state, it will receive data from a \clean{} cache
and no store requests can be processed when the data is in transit (by
Invariant~\ref{noTransitWrite}). Therefore, by the induction hypothesis it has
the up-to-date data.
